iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-13 manuscript/main.tex
changed back

\section*{Acknowledgements}
We thank organizers and participants at the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for helpful suggestions.
\vspace*{-12pt}

>>>>

\section*{Acknowledgements}
We thank the organizers and participants at the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for their helpful suggestions.
\vspace*{-12pt}
